---
title       : Using Shiny for interactive plots of Sunshine hours in the UK
subtitle    : Source - the UK's National Weather Service
author      : Oleg Efimov
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : standalone # {selfcontained, draft}
knit        : slidify::knit2slides
---

## What is Shiny?

It is a web application framework for R.

Shiny apps are easy to write. No web development skills are required.

Shiny combines the computational power of R with the interactivity of the modern web. 

In this example we wil use time-series of monthly, seasonal and annual regional sunshine values published by the UK's National Weather Service as a data source and power of R code and Shiny to create an interactive plots of total hours of sunshine in the UK by month or by years range.

---
## Computations
Regular R code is used for a computation in shiny apps.

``` {r echo=FALSE }
library(slidify)
library(reshape)
library(ggplot2)
```

```{r}
#Loading weather stats
sh <- read.csv(
  "http://www.metoffice.gov.uk/pub/data/weather/uk/climate/datasets/Sunshine/date/UK.txt", 
  skip = 7, sep = "")
dim(sh)
#Subsetting data
sh <- sh[1:86,1:13]
sh <- melt(sh,id='Year', variable_name = "Month")
dim(sh)
```

---
## Plots in Shiny
Using inputs in a web page allows to create interactive plots 

```{r echo=FALSE}
sh_sub <- sh[sh$Month=='JUN',]
qplot(Year,value,data = sh_sub, xlab = "Year", ylab = "Sunshine (total hours)", main = 'JUN') 

```

---
## Plots in Shiny
``` {r echo=FALSE}
sh_range <- sh[sh$Year>=1930 & sh$Year<=2010,]
#drawing a plot
qplot(Year,value,data = sh_range, color = Month, xlab = "Year", ylab = "Sunshine (total hours)")
```
